\bf Range Analysis for the IonMonkey JavaScript engine

### 2012-05-01 project-writings/paper.tex
if we're going to use valid python, it should be valid python. I'm done now.

# Replace all uses of the instruction x that are dominated by
# the instruction x_prime with x_prime
def replaceDominatedUses(x, x_prime):
  for each use in x.uses():
    ins = use.instruction()
    if ins != x_prime and isDominatedUse(x_prime, use):
      replaceUseWith(use, x_prime)

@@

def blockDominates(b1, b2):
  high = b1.domIndex() + b1.numDominated()
  low  = b1.domIndex()
  return b2.domIndex() >= low and b2.domIndex <= high
\end{lstlisting}

>>>>

# Replace all uses of the instruction x that are dominated by
# the instruction x_prime with x_prime
def replaceDominatedUses(x, x_prime):
  for use in x.uses():
    ins = use.instruction()
    if ins != x_prime and isDominatedUse(x_prime, use):
      replaceUseWith(use, x_prime)

@@

def blockDominates(b1, b2):
  high = b1.domIndex() + b1.numDominated()
  low  = b1.domIndex()
  return b2.domIndex() >= low and b2.domIndex() <= high
\end{lstlisting}
